Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-01 paper/paper.tex
notation changes.

% Maths operators
\newcommand{\nds}{\operatorname{nds}}
\newcommand{\paths}{\operatorname{paths}}
\newcommand{\lessnonind}[1]{\prescript{}{#1}{\rightarrowtail}\ }
\newcommand{\lessind}[1]{\prescript{}{#1}{\hookrightarrow}\ }
\newcommand{\lessmap}[1]{\prescript{}{#1}{\mapsto}\ }
\newcommand{\lesspreceq}[1]{\prescript{}{#1}{\preceq}\ }
\newcommand{\V}{\operatorname{V}}
% to do comments
\usepackage{color}
\newcommand{\todo}[1]{{\color{red} {[}{#1}{]}}}

@@

A vertex $q$ which is adjacent to $p$ is called its \emph{neighbour}.  Let $N(p) = \{ q \in \V(P) :
 p \text{ and } q \text{ are adjacent }\}$ be the set of neighbours of $p$.  The \emph{neighbourhood
degree sequence} (NDS) of $p$, $\nds(p)$, is the (non-ascending) sequence of degrees of its
neighbours.

@@

Also, $p \lessmap{k} t$ implies that for each $q \in N(p)\setminus P_k$, where $P_k$
is some subset of $P$ with $|P_k| \leq k$, $q \lessmap{k} u$, where $u \in N(t)$ and
each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by Proposition 1.  Hence $\nds(p)
\lesspreceq{k} \nds(t)$.
\end{proof}

@@

\begin{proposition}
    Let $p,q \in \V(P)$ and $t,u\in \V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
     $\paths(p, q, 2) - k \le \paths(t, u, 2)$.
\end{proposition}
\begin{proof}
Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
\begin{align*}
P_{2} = & \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \} \\
 = & \{((p,x),(x,q)) : x\in N(p) \text{ and } x\in N(q) \} \\
 = & \{((p,x),(x,q)) : x\in N(p)\cap N(q) \} .
\end{align*}
So $\paths(p,q,2) = | N(p)\cap N(q)| \leq deg(p)$.

If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$
\[
|N(p)\cap N(q)| - k \leq deg(p) - k \leq deg(t).
\]
As $|N(p)\cap N(q)|\leq deg(p) \leq |N(t)\cap N(u)|\leq deg(t)$, we have
\[
|N(p)\cap N(q)| - k \leq deg(p) - k\leq |N(t)\cap N(u)|\leq deg(t)
\]
which is
\[
\paths(p, q, 2) - k \leq \paths(t, u, 2).
\]
\end{proof}

@@

\begin{proposition}
    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\V(G)$. The
    vertices $p$ and $q$ in $G^{n, \ell}$ are adjacent, if there are at least $n$ simple paths of
    length exactly $\ell$ between $p$ and $q$ in $G$. Then any $k$-less-subgraph isomorphism
    $P \lessnonind{k} T$ induces a new $k$-less-subgraph isomorphism
    $P^{n, 2}\lessnonind{k} T^{n - k, 2}$.
\end{proposition}

>>>>

% Maths operators
\newcommand{\paths}{\operatorname{paths}}
\newcommand{\lessnonind}[1]{\prescript{}{#1}{\rightarrowtail}\ }
\newcommand{\lessind}[1]{\prescript{}{#1}{\hookrightarrow}\ }
\newcommand{\lessmap}[1]{\prescript{}{#1}{\mapsto}\ }
\newcommand{\lesspreceq}[1]{\prescript{}{#1}{\preceq}\ }
\newcommand{\V}{\operatorname{V}}
\newcommand{\N}{\operatorname{N}}
\newcommand{\nds}{\operatorname{S}}
% to do comments
\usepackage{color}
\newcommand{\todo}[1]{{\color{red} {[}{#1}{]}}}

@@

A vertex $q$ which is adjacent to $p$ is called its \emph{neighbour}.  Let $\N(p) = \{ q \in \V(P) :
 p \text{ and } q \text{ are adjacent }\}$ be the set of neighbours of $p$.  The \emph{neighbourhood
degree sequence} (NDS) of $p$, $\nds(p)$, is the (non-ascending) sequence of degrees of its
neighbours.

@@

Also, $p \lessmap{k} t$ implies that for each $q \in \N(p)\setminus P_k$, where $P_k$
is some subset of $P$ with $|P_k| \leq k$, $q \lessmap{k} u$, where $u \in \N(t)$ and
each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by Proposition 1.  Hence $\nds(p)
\lesspreceq{k} \nds(t)$.
\end{proof}

@@

\begin{proposition}
    Let $p,q \in \V(P)$ and $t,u\in \V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
     $\paths(p, q, 2) - k \le \paths(t, u, 2)$.
\end{proposition}
\begin{proof}
Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
\begin{align*}
P_{2} = & \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \} \\
 = & \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \} \\
 = & \{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \} .
\end{align*}
So $\paths(p,q,2) = | \N(p)\cap \N(q)| \leq deg(p)$.

If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$
\[
|\N(p)\cap \N(q)| - k \leq deg(p) - k \leq deg(t).
\]
As $|\N(p)\cap \N(q)|\leq deg(p) \leq |\N(t)\cap \N(u)|\leq deg(t)$, we have
\[
|\N(p)\cap \N(q)| - k \leq deg(p) - k\leq |\N(t)\cap \N(u)|\leq deg(t)
\]
which is
\[
\paths(p, q, 2) - k \leq \paths(t, u, 2).
\]
\end{proof}

@@

\begin{proposition}
    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\V(G)$. The
    vertices $p$ and $q$ in $G^{n, \ell}$ are adjacent, if there are at least $n$ simple paths of
    length exactly $\ell$ between $p$ and $q$ in $G$. Then any $k$-less-subgraph isomorphism
    $P \lessnonind{k} T$ induces a new $k$-less-subgraph isomorphism
    $P^{n+k, 2}\lessnonind{k} T^{n, 2}$.
\end{proposition}
